---
title: "AK_Harbor_Porpoises_SNP_DAPCs"
author: "Samuel May"
date: "3/30/2020"
output:
  pdf_document: default
  html_document: default
---

# Alaska Harbor Porpoises: NGOS Project to explore population structure of Harbor Porpoises in Southeast Alaska


## Requirements:
Must load workspace from Data_Exploration_Basic_Stats_and_Filtering script

```{r, message=FALSE,results="hide",warning=F}
#Session > Set Working Directory > to Source File Location

setwd("G:/My Drive/Southeast AK Harbor Porpoise Structure/R_Project/Scripts")
#install.packages("remotes")
#remotes::install_github("romunov/zvau")
library(zvau)

library(tidyverse)
library(genetics)
library(adegenet)
library(hierfstat)
library(adespatial)
library(devtools)
library(RColorBrewer)
library(usedist)
library(graph4lg)
library(xlsx)
library(parallel)
library(foreach)
library(doParallel)
library(pander)
library(LEA)
library(ggpubr)
library(diveRsity)
library(usedist)

load("SNP_Data_Exploration_Basic_Stats_and_Filtering_Workspace.RData")

```

Data: **292SNP GTseq panel** + **Q_Ppho strata metadata**
Run Data_Exploration Script first and use defined genind objects from there.


# DAPCs By a priori Strata

## Strata 1
```{r}
Strata1_genepop<-AK_genepop
Strata1_genepop$pop<-as.factor(Strata1_genepop$other$Strata1)
Strata1_genepop<-Strata1_genepop[!Strata1_genepop$pop=="WESTERN_BS"]

table(Strata1_genepop$pop) 
Strata1_DAPC<- dapc(Strata1_genepop,pop=Strata1_genepop$pop,n.pca = 65,n.da=3) #Retain most and identify optimal
a_score_strata1<-optim.a.score(Strata1_DAPC,n.sim=1000)
Strata1_DAPC<- dapc(Strata1_genepop,pop=Strata1_genepop$pop,n.pca = a_score_strata1$best,n.da=3)

scatter(Strata1_DAPC,1,2,grp = Strata1_genepop$pop,pch=16,
        posi.da="bottomleft",col=brewer.pal(4,"Dark2"),
        legend=T, clabel = 0,ratio.da = .25,
        posi.pca = "bottomright",scree.pca = T)
mtext(text= "Strata 1", side = 3,adj = -20,padj = -1,cex = 2.5)

find.clusters(Strata1_genepop,n.pca = a_score_strata1$best)

Strata1_DAPC$var  ### Proportion of variance conserved by the principal components (36.4%)
Strata1_DAPC$prior #### Numeric vector giving prior group probabilities, low likely because of sample size

```


Corresponding Structure Plot Strata 1
```{r}
#convert genind2structure and structure2geno ... there might be a more direct way of doing this, but this works


genind2structure(Strata1_genepop,file = "../Data/STRUCTURE/AK_genepop_Strata1.STRUCTURE",pops = T)
#using this new function excludes ind and pop labels from row 1, so added those manually for now
struct2geno(input.file = "../Data/STRUCTURE/AK_genepop_Strata1.STRUCTURE", ploidy = 2, extra.row = 1, extra.column = 4, FORMAT = 2)


obj.snmf.1a <- snmf(input.file = "../Data/STRUCTURE/AK_genepop_Strata1.STRUCTURE.geno", K =
1:10,repetitions = 1, alpha = 100,iterations = 10000, project = "new",entropy = TRUE)
plot(obj.snmf.1, col = "blue4", cex = 1.4, pch = 19) #how many groups are optimal? 1...

obj.snmf.1b <- snmf(input.file = "../Data/STRUCTURE/AK_genepop_Strata1.STRUCTURE.geno", K =
nPop(Strata1_genepop),repetitions = 1, alpha = 100,iterations = 10000, project = "new")
qmatrix.1b <- as.data.frame(Q(obj.snmf.1b,K=nPop(Strata1_genepop)))
rownames(qmatrix.1b)<-indNames(Strata1_genepop)
colnames(qmatrix.1b)<-popNames(Strata1_genepop)
qmatrix.1b<-qmatrix.1b[base::order(qmatrix.1b$CHUK,qmatrix.1b$EASTERN_BS,qmatrix.1b$GOA),]

colz<-viridis::viridis(nPop(Strata1_genepop))

barplot(t(qmatrix.1b), col = colz, border = NA, space = 0,axes=F,xaxt="n")
axis(side=2)
mtext(side=3,"Strata1 snmf Proportions",cex=1.5)
par(xpd=NA)
legend(x = 15,y=-.05,fill = colz,legend=popNames(Strata1_genepop),ncol= 2)



```
This structure plot is not useful, using the deltaK method would yield one optimal cluster.


## Strata 2
excluding 3 kodiak individuals
```{r}
AK_genepop$pop<-as.factor(AK_genepop$other$Strata2)
Strata2_genepop<-AK_genepop[which(is.na(AK_genepop$pop)==F)]
Strata2_genepop<-AK_genepop[!AK_genepop$other$Strata3%in%c("KODIAK","WBS","YAKUTAT")]
table(Strata2_genepop$other$Strata2) 


Strata2_DAPC<- dapc(Strata2_genepop,pop=Strata2_genepop$pop,n.pca = 60,n.da=3) #Retain most and identify optimal
a_score_strata2<-optim.a.score(n.sim=1000,Strata2_DAPC)
Strata2_DAPC<- dapc(Strata2_genepop,pop=Strata2_genepop$pop,n.pca = a_score_strata2$best ,n.da = 3) #Retain most and identify optimal

scatter(Strata2_DAPC,1,2,grp = Strata2_genepop$pop,pch=16,
        posi.da="topright",
        col=brewer.pal(nPop(Strata2_genepop),"Dark2"),
        legend=T, clabel = 0,ratio.da = .25,
        posi.pca = "bottomright",scree.pca = T,
        posi.leg="bottomleft")
mtext(text= "Strata 2", side = 3,adj = -20,padj = -1,cex = 2.5)


find.clusters(Strata2_genepop,n.pca = a_score_strata2$best)

Strata2_DAPC$var  ### Proportion of variance conserved by the principal components (36.4%)
Strata2_DAPC$prior #### Numeric vector giving prior group probabilities, low likely because of sample size
```

Corresponding Structure Plot Strata 2
```{r}
#convert genind2structure and structure2geno ... there might be a more direct way of doing this, but this works


genind2structure(Strata2_genepop,file = "../Data/STRUCTURE/AK_genepop_Strata2.STRUCTURE",pops = T)
#using this new function excludes ind and pop labels from row 1, so added those manually for now
struct2geno(input.file = "../Data/STRUCTURE/AK_genepop_Strata2.STRUCTURE", ploidy = 2, extra.row = 1, extra.column = 4, FORMAT = 2) 


obj.snmf.2a <- snmf(input.file = "../Data/STRUCTURE/AK_genepop_Strata2.STRUCTURE.geno", K =
1:10,repetitions = 1, alpha = 100,iterations = 10000, project = "new",entropy = TRUE,CPU = 3)
plot(obj.snmf.2a, col = "blue4", cex = 1.4, pch = 19) #ONE optimal group

obj.snmf.2b <- snmf(input.file = "../Data/STRUCTURE/AK_genepop_Strata2.STRUCTURE.geno", K =
nPop(Strata2_genepop),repetitions = 1, alpha = 100,iterations = 10000, project = "new",CPU = 3)
qmatrix.2b <- as.data.frame(Q(obj.snmf.2b,K=nPop(Strata2_genepop)))
rownames(qmatrix.2b)<-indNames(Strata2_genepop)
colnames(qmatrix.2b)<-popNames(Strata2_genepop)
qmatrix.2b<-qmatrix.2b[base::order(qmatrix.2b$WBS,qmatrix.2b$BAR,qmatrix.2b$EBS,qmatrix.2b$WGOA,qmatrix.2b$YAKUTAT,qmatrix.2b$WGOA),]

colz<-viridis::viridis(nPop(Strata2_genepop))

barplot(t(qmatrix.2b), col = colz, border = NA, space = 0,axes=F,xaxt="n")
axis(side=2)
mtext(side=3,"Strata2 snmf Proportions",cex=1.5)
par(xpd=NA)
legend(x = 15,y=-.05,fill = colz,legend=popNames(Strata2_genepop),ncol= 2)

Strata2_genepop$pop
indNames(Strata2_genepop)
```
This structure plot is not useful, using the deltaK method would yield one optimal cluster.


## Strata 3

```{r}
AK_genepop$pop<-as.factor(AK_genepop$other$Strata3)
Strata3_genepop<-AK_genepop[which(is.na(AK_genepop$pop)==F)]
table(Strata3_genepop$pop)

Strata3_DAPC<- dapc(Strata3_genepop,pop=Strata3_genepop$pop,n.pca=60,n.da=8) #Retain most and identify optimal
a_score_strata3<-optim.a.score(n.sim=1000,Strata3_DAPC)
Strata3_DAPC<- dapc(Strata2_genepop,pop=Strata3_genepop$pop,n.pca = a_score_strata3$best ,n.da = 5) #Retain most and identify optimal


colz<-c("gold","tan","green","blue","black","purple","hotpink","orange","black")

scatter(Strata3_DAPC,1,2,grp = Strata3_genepop$pop,pch=16,
        posi.da="bottomleft",
        col=colz,
        legend=T, clabel = 0,ratio.da = .25,
        posi.pca = "topright",scree.pca = T,
        posi.leg = "bottomright")


find.clusters(Strata3_genepop,n.pca = a_score_strata3$best)


```

Same as above Strata3 but excluding those with <5 samples:
```{r}
pop_counts<-table(Strata3_genepop$pop)
exclude_pops<-names(pop_counts[which(pop_counts<5)])
exclude_pops
Strata3_genepop_filtered<-Strata3_genepop[which(!Strata3_genepop$pop%in%exclude_pops)]

Strata3_DAPC_filtered<-dapc(Strata3_genepop_filtered,pop=Strata3_genepop_filtered$pop,n.pca=50,n.da=4) #Retain most and identify optimal
a_score_strata3_filtered<-optim.a.score(n.sim=1000,Strata3_DAPC_filtered)
Strata3_DAPC_filtered<- dapc(Strata3_genepop_filtered,pop=Strata3_genepop_filtered$pop,n.pca = a_score_strata3_filtered$best ,n.da = 5) #Retain most and identify optimal



colz<-c("gold","tan","green","blue","black")

scatter(Strata3_DAPC_filtered,1,2,grp = Strata3_genepop_filtered$pop,pch=16,
        posi.da="bottomleft",
        col=colz,
        legend=T, clabel = 0,ratio.da = .25,
        posi.pca = "topright",scree.pca = T,
        posi.leg = "bottomright")

find.clusters(Strata3_genepop_filtered,n.pca = a_score_strata3_filtered$best)

Strata3_DAPC_filtered$var  ### Proportion of variance conserved by the principal components (36.4%)
Strata3_DAPC_filtered$prior #### Numeric vector giving prior group probabilities, low likely because of sample size

```
Corresponding Structure Plot Strata 3 filtered
```{r}
#convert genind2structure and structure2geno ... there might be a more direct way of doing this, but this works


genind2structure(Strata3_genepop_filtered,file = "../Data/STRUCTURE/AK_genepop_Strata3.STRUCTURE",pops = T)
#using this new function excludes ind and pop labels from row 1, so added those manually for now
struct2geno(input.file = "../Data/STRUCTURE/AK_genepop_Strata3.STRUCTURE", ploidy = 2, extra.row = 1, extra.column = 4, FORMAT = 2) 


obj.snmf.3a <- snmf(input.file = "../Data/STRUCTURE/AK_genepop_Strata3.STRUCTURE.geno", K =
1:10,repetitions = 1, alpha = 100,iterations = 10000, project = "new",entropy = TRUE,CPU = 3)
plot(obj.snmf.3a, col = "blue4", cex = 1.4, pch = 19) #ONE, maybe 2 optimal groups... I was hopeful for this one :(

obj.snmf.3b <- snmf(input.file = "../Data/STRUCTURE/AK_genepop_Strata3.STRUCTURE.geno", K =
nPop(Strata3_genepop_filtered),repetitions = 1, alpha = 100,iterations = 10000, project = "new",CPU = 3)
qmatrix.3b <- as.data.frame(Q(obj.snmf.3b,K=nPop(Strata3_genepop_filtered)))
rownames(qmatrix.3b)<-indNames(Strata3_genepop_filtered)
colnames(qmatrix.3b)<-popNames(Strata3_genepop_filtered)
qmatrix.3b<-qmatrix.3b[base::order(qmatrix.3b$BARROW,qmatrix.3b$NEBS,qmatrix.3b$COOK,qmatrix.3b$COPPER,qmatrix.3b$N_SEAK),]

colz<-viridis::viridis(nPop(Strata3_genepop_filtered))

barplot(t(qmatrix.3b), col = colz, border = NA, space = 0,axes=F,xaxt="n")
axis(side=2)
mtext(side=3,"Strata3 snmf Proportions",cex=1.5)
par(xpd=NA)
legend(x = 15,y=-.05,fill = colz,legend=popNames(Strata3_genepop_filtered),ncol= 2)

Strata3_genepop$pop
indNames(Strata3_genepop_filtered)
```

## Southern AK DAPC

```{r, warning=F}
South_AK_genepop<-Strata3_genepop_filtered[which(!Strata3_genepop_filtered$pop%in%c("BARROW"))]
table(South_AK_genepop$pop) 

South_AK_DAPC<- dapc(South_AK_genepop,pop=South_AK_genepop$pop,n.pca=45,n.da=7) #Retain most and identify optimal
a_score_south_AK<-optim.a.score(n.sim=1000,South_AK_DAPC)
South_AK_DAPC<- dapc(South_AK_genepop,pop=South_AK_genepop$pop,n.pca = a_score_south_AK$best ,n.da = 5) #Retain most and identify optimal


colz<-c("tan","green","blue","black")


scatter(South_AK_DAPC,1,2,grp = South_AK_genepop$pop,pch=16,
        posi.da="topright",
        col=colz,
        legend=T, clabel = 0,ratio.da = .25,
        posi.pca = "bottomright",scree.pca = T,
        posi.leg = "bottomleft")

find.clusters(South_AK_genepop,n.pca = a_score_south_AK$best)

South_AK_DAPC$var  ### Proportion of variance conserved by the principal components (36.4%)
South_AK_DAPC$prior #### Numeric vector giving prior group probabilities, low likely because of sample size
```

Corresponding Structure Plot South AK filtered
```{r}
#convert genind2structure and structure2geno ... there might be a more direct way of doing this, but this works


genind2structure(South_AK_genepop,file = "../Data/STRUCTURE/AK_genepop_South_AK.STRUCTURE",pops = T)
#using this new function excludes ind and pop labels from row 1, so added those manually for now
struct2geno(input.file = "../Data/STRUCTURE/AK_genepop_South_AK.STRUCTURE", ploidy = 2, extra.row = 1, extra.column = 4, FORMAT = 2) 


obj.snmf.Sa <- snmf(input.file = "../Data/STRUCTURE/AK_genepop_South_AK.STRUCTURE.geno", K =
1:10,repetitions = 1, alpha = 100,iterations = 10000, project = "new",entropy = TRUE,CPU = 3)
plot(obj.snmf.Sa, col = "blue4", cex = 1.4, pch = 19) #ONE, maybe 2 optimal groups... I was hopeful for this one :(

obj.snmf.Sb <- snmf(input.file = "../Data/STRUCTURE/AK_genepop_South_AK.STRUCTURE.geno", K =
nPop(South_AK_genepop),repetitions = 1, alpha = 100,iterations = 10000, project = "new",CPU = 3)
qmatrix.Sb <- as.data.frame(Q(obj.snmf.Sb,K=nPop(South_AK_genepop)))
rownames(qmatrix.Sb)<-indNames(South_AK_genepop)
colnames(qmatrix.Sb)<-popNames(South_AK_genepop)
qmatrix.Sb<-qmatrix.Sb[base::order(qmatrix.Sb$NEBS,qmatrix.Sb$COOK,qmatrix.Sb$COPPER,qmatrix.Sb$N_SEAK),]

colz<-viridis::viridis(nPop(South_AK_genepop))

barplot(t(qmatrix.Sb), col = colz, border = NA, space = 0,axes=F,xaxt="n")
axis(side=2)
mtext(side=3,"Strata3 snmf Proportions",cex=1.5)
par(xpd=NA)
legend(x = 15,y=-.05,fill = colz,legend=popNames(South_AK_genepop),ncol= 2)

South_AK_genepop$pop
indNames(South_AK_genepop)
```
This one is actually a bit interesting, as it shows potential admixture within the GOA and NEBS... but still not very useful. K=1

Combined Plotting of DAPCs by strata:

```{r}
par(mfrow=c(2,2))
#Strata 1
scatter(Strata1_DAPC,1,2,grp = Strata1_genepop$pop,pch=16,
        posi.da="bottomleft",col=brewer.pal(4,"Dark2"),
        legend=T, clabel = 0,ratio.da = .25,
        posi.pca = "bottomright",scree.pca = T,
        posi.leg = "topleft")
mtext(text= "A", side = 3,adj = -3,padj = -2.5,cex = 1.3)

#Strata 2
scatter(Strata2_DAPC,1,2,grp = Strata2_genepop$pop,pch=16,
        posi.da="bottomleft",
        col=brewer.pal(nPop(Strata2_genepop),"Dark2"),
        legend=T, clabel = 0,ratio.da = .25,
        posi.pca = "bottomright",scree.pca = T,
        posi.leg="topleft")
mtext(text= "B", side = 3,adj = -3,padj = -2.5,cex = 1.3)

#Strata 3 (filtered >5)
colz<-c("gold","tan","green","blue","black")
scatter(Strata3_DAPC_filtered,1,2,grp = Strata3_genepop_filtered$pop,pch=16,
        posi.da="bottomleft",
        col=colz,
        legend=T, clabel = 0,ratio.da = .25,
        posi.pca = "bottomright",scree.pca = T,
        posi.leg = "topleft")
mtext(text= "C", side = 3,adj = -3,padj = -2.5,cex = 1.3)

#Southern AK
colz<-c("tan","green","blue","black")

scatter(South_AK_DAPC,1,2,grp = South_AK_genepop$pop,pch=16,
        posi.da="bottomleft",
        col=colz,
        legend=T, clabel = 0,ratio.da = .25,
        posi.pca = "bottomright",scree.pca = T,
        posi.leg = "topleft")
mtext(text= "D", side = 3,adj =-3,padj = -2.5,cex = 1.3)

```


Combined plotting of STRUCTURE plots for 4 strata:
```{r STRUCTURE_PLOTS_BASE_R}
par(mfrow=c(2,2),mar=c(4,0,1.5,0),oma=c(1,3.5,0,0))

colz<-viridis::viridis(nPop(Strata1_genepop))

barplot(t(qmatrix.1b), col = colz, border = NA, space = 0,axes=F,xaxt="n",main="Strata1")
axis(side=2)
mtext(side=2,"Admixture Coef.",cex=1,line = 2)
par(xpd=NA)
legend(x = 3,y=-.05,fill = colz,legend=popNames(Strata1_genepop),ncol= 2)

colz<-viridis::viridis(nPop(Strata2_genepop))

barplot(t(qmatrix.2b), col = colz, border = NA, space = 0,axes=F,xaxt="n",main="Strata 2")
#axis(side=2)
#mtext(side=3,"snmf Proportions",cex=1.5)
par(xpd=NA)
legend(x = 13,y=-.05,fill = colz,legend=popNames(Strata2_genepop),ncol= 2)

colz<-viridis::viridis(nPop(Strata3_genepop_filtered))

barplot(t(qmatrix.3b), col = colz, border = NA, space = 0,axes=F,xaxt="n", main="Strata 3")
axis(side=2)
mtext(side=2,"Admixture Coef.",cex=1,line=2)
par(xpd=NA)
legend(x = 10,y=-.05,fill = colz,legend=popNames(Strata3_genepop_filtered),ncol= 2)


colz<-viridis::viridis(nPop(South_AK_genepop))

barplot(t(qmatrix.Sb), col = colz, border = NA, space = 0,axes=F,xaxt="n",main="South Alaska")
#axis(side=2)
#mtext(side=3,"Strata3 snmf Proportions",cex=1.5)
par(xpd=NA)
legend(x = 10,y=-.05,fill = colz,legend=popNames(South_AK_genepop),ncol= 2)



```
The above admixture plots are sorted by *posteriori* group assignments, not by priors. below I redo this in ggplot for more intuitive plots sorted by prior group assignment (Also sorted within groups by lat and long)

```{r STRUCTURE_PLOTS_gg}

###STRATA 1
qmatrix.1b_gg<-qmatrix.1b
qmatrix.1b_gg$prior<-Strata1_genepop$pop[match(rownames(qmatrix.1b_gg),indNames(Strata1_genepop))]
qmatrix.1b_gg$lat<-Strata1_genepop$other$xy$y[match(rownames(qmatrix.1b_gg),indNames(Strata1_genepop))]
qmatrix.1b_gg$long<-Strata1_genepop$other$xy$x[match(rownames(qmatrix.1b_gg),indNames(Strata1_genepop))]
qmatrix.1b_gg<-rownames_to_column(qmatrix.1b_gg,"labID")

qmatrix.1b_gg<-qmatrix.1b_gg %>% gather(key = "posterior",value = "coef",CHUK,EASTERN_BS,GOA)
qmatrix.1b_gg<-qmatrix.1b_gg[base::order(qmatrix.1b_gg$long,qmatrix.1b_gg$lat,qmatrix.1b_gg$labID,qmatrix.1b_gg$prior),]
qmatrix.1b_gg$labID<-factor(qmatrix.1b_gg$labID,levels = unique(qmatrix.1b_gg$labID))
qmatrix.1b_gg$prior<-factor(qmatrix.1b_gg$prior,levels = c("CHUK","EASTERN_BS","GOA"))


structure_strata1 <- qmatrix.1b_gg %>% 
  ggplot(aes(x=labID,y=coef,fill=posterior,col=posterior)) +
  geom_bar(position="fill", stat="identity") + 
  xlab("") + ylab("Admixture Coefficient") +
  theme(axis.text.x= element_blank(),
        axis.ticks.x= element_blank(),
        panel.spacing = unit(0, "lines"),
        legend.position="bottom") +
  facet_grid(~prior, scales="free",space="free_x",switch = "x") + 
  scale_y_continuous(expand = c(0, 0), limits = c(0, 1))

###STRATA 2
qmatrix.2b_gg<-qmatrix.2b
qmatrix.2b_gg$prior<-Strata2_genepop$pop[match(rownames(qmatrix.2b_gg),indNames(Strata2_genepop))]
qmatrix.2b_gg$lat<-Strata2_genepop$other$xy$y[match(rownames(qmatrix.2b_gg),indNames(Strata2_genepop))]
qmatrix.2b_gg$long<-Strata2_genepop$other$xy$x[match(rownames(qmatrix.2b_gg),indNames(Strata2_genepop))]
qmatrix.2b_gg<-rownames_to_column(qmatrix.2b_gg,"labID")

qmatrix.2b_gg<-qmatrix.2b_gg %>% gather(key = "posterior",value = "coef",BAR,EBS,EGOA,WGOA)
qmatrix.2b_gg<-qmatrix.2b_gg[base::order(qmatrix.2b_gg$long,qmatrix.2b_gg$lat,qmatrix.2b_gg$labID,qmatrix.2b_gg$prior),]
qmatrix.2b_gg$labID<-factor(qmatrix.2b_gg$labID,levels = unique(qmatrix.2b_gg$labID))
qmatrix.2b_gg$prior<-factor(qmatrix.2b_gg$prior,levels = c("BAR","EBS","EGOA","WGOA"))


structure_Strata2 <- qmatrix.2b_gg %>% 
  ggplot(aes(x=labID,y=coef,fill=posterior,col=posterior)) +
  geom_bar(position="fill", stat="identity") + 
  xlab("") + ylab("") +
  theme(axis.text.x= element_blank(),
        axis.ticks.x= element_blank(),
        panel.spacing = unit(0, "lines"),
        legend.position="bottom") +
  facet_grid(~prior, scales="free",space="free_x",switch = "x") + 
  scale_y_continuous(expand = c(0, 0), limits = c(0, 1))



###STRATA 3
qmatrix.3b_gg<-qmatrix.3b
qmatrix.3b_gg$prior<-Strata3_genepop_filtered$pop[match(rownames(qmatrix.3b_gg),indNames(Strata3_genepop_filtered))]
qmatrix.3b_gg$lat<-Strata3_genepop_filtered$other$xy$y[match(rownames(qmatrix.3b_gg),indNames(Strata3_genepop_filtered))]
qmatrix.3b_gg$long<-Strata3_genepop_filtered$other$xy$x[match(rownames(qmatrix.3b_gg),indNames(Strata3_genepop_filtered))]
qmatrix.3b_gg<-rownames_to_column(qmatrix.3b_gg,"labID")

qmatrix.3b_gg<-qmatrix.3b_gg %>% gather(key = "posterior",value = "coef",BARROW,NEBS,COOK,COPPER,N_SEAK)
qmatrix.3b_gg<-qmatrix.3b_gg[base::order(qmatrix.3b_gg$long,qmatrix.3b_gg$lat,qmatrix.3b_gg$labID,qmatrix.3b_gg$prior),]
qmatrix.3b_gg$labID<-factor(qmatrix.3b_gg$labID,levels = unique(qmatrix.3b_gg$labID))
qmatrix.3b_gg$prior<-factor(qmatrix.3b_gg$prior,levels = c("BARROW","NEBS","COOK","COPPER","N_SEAK"))

structure_Strata3 <- qmatrix.3b_gg %>% 
  ggplot(aes(x=labID,y=coef,fill=posterior,col=posterior)) +
  geom_bar(position="fill", stat="identity") + 
  xlab("") + ylab("Admixture Coefficient") +
  theme(axis.text.x= element_blank(),
        axis.ticks.x= element_blank(),
        panel.spacing = unit(0, "lines"),
        legend.position="bottom") +
  facet_grid(~prior, scales="free",space="free_x",switch = "x") + 
  scale_y_continuous(expand = c(0, 0), limits = c(0, 1))


###South AK
qmatrix.Sb_gg<-qmatrix.Sb
qmatrix.Sb_gg$prior<-South_AK_genepop$pop[match(rownames(qmatrix.Sb_gg),indNames(South_AK_genepop))]
qmatrix.Sb_gg$lat<-South_AK_genepop$other$xy$y[match(rownames(qmatrix.Sb_gg),indNames(South_AK_genepop))]
qmatrix.Sb_gg$long<-South_AK_genepop$other$xy$x[match(rownames(qmatrix.Sb_gg),indNames(South_AK_genepop))]
qmatrix.Sb_gg<-rownames_to_column(qmatrix.Sb_gg,"labID")

qmatrix.Sb_gg<-qmatrix.Sb_gg %>% gather(key = "posterior",value = "coef",NEBS,COOK,COPPER,N_SEAK)
qmatrix.Sb_gg<-qmatrix.Sb_gg[base::order(qmatrix.Sb_gg$long,qmatrix.Sb_gg$lat,qmatrix.Sb_gg$labID,qmatrix.Sb_gg$prior),]
qmatrix.Sb_gg$labID<-factor(qmatrix.Sb_gg$labID,levels = unique(qmatrix.Sb_gg$labID))
qmatrix.Sb_gg$prior<-factor(qmatrix.Sb_gg$prior,levels = c("NEBS","COOK","COPPER","N_SEAK"))

structure_South_AK <- qmatrix.Sb_gg %>% 
  ggplot(aes(x=labID,y=coef,fill=posterior,col=posterior)) +
  geom_bar(position="fill", stat="identity") + 
  xlab("") + ylab("") +
  theme(axis.text.x= element_blank(),
        axis.ticks.x= element_blank(),
        panel.spacing = unit(0, "lines"),
        legend.position="bottom") +
  facet_grid(~prior, scales="free",space="free_x",switch = "x") + 
  scale_y_continuous(expand = c(0, 0), limits = c(0, 1))


ggarrange(structure_strata1,structure_Strata2,structure_Strata3,structure_South_AK,labels="AUTO",hjust = -4.5 )

```


Which Loci contribute most to between cluster variance?
```{r DAPC_LOADINGS}
# We can assess which alleles pull apart the DAPC clusters using the command loadingplot. 

par(mfrow=c(4,2),mar=c(1,1,1,1),oma=c(0,3,0,0))
#Strata1
#Along Axis 1
contrib1.1 <- loadingplot(Strata1_DAPC$var.contr, axis = 1, lab.jitter = 1,threshold = .01,xlab = "",main="Strata1, DA1")
# Along Axis 2
contrib1.2 <- loadingplot(Strata1_DAPC$var.contr, axis = 2, lab.jitter = 1,threshold = .01,xlab="",main="Strata1, DA2")
#Strata2
#Along Axis 1
contrib2.1 <- loadingplot(Strata2_DAPC$var.contr, axis = 1, lab.jitter = 1,threshold = .01,xlab = "",main="Strata2, DA1")
# Along Axis 2
contrib2.2 <- loadingplot(Strata2_DAPC$var.contr, axis = 2, lab.jitter = 1,threshold = .01,xlab="",main="Strata2, DA2")

#Strata3
#Along Axis 1
contrib3.1 <- loadingplot(Strata3_DAPC_filtered$var.contr, axis = 1, lab.jitter = 1,threshold = .01,xlab = "",main="Strata3, DA1")
# Along Axis 2
contrib3.2 <- loadingplot(Strata3_DAPC_filtered$var.contr, axis = 2, lab.jitter = 1,threshold = .01,xlab="",main="Strata3, DA2")

#South AK
#Along Axis 1
contribS.1 <- loadingplot(South_AK_DAPC$var.contr, axis = 1, lab.jitter = 1,threshold = .01,xlab = "",main="South AK, DA1")
# Along Axis 2
contribS.2 <- loadingplot(South_AK_DAPC$var.contr, axis = 2, lab.jitter = 1,threshold = .01,xlab="",main="South AK, DA2")

mtext(text = "DAPC Loadings", side=2,outer=T,line=1.5)









#loading threshold for a diagnostic locus:  0.01 
da1.1_diagnostic_loci<-contrib1.1$var.names[contrib1.1$var.values>0.01]
da1.2_diagnostic_loci<-contrib1.2$var.names[contrib1.2$var.values>0.01]
da2.1_diagnostic_loci<-contrib2.1$var.names[contrib2.1$var.values>0.01]
da2.2_diagnostic_loci<-contrib2.2$var.names[contrib2.2$var.values>0.01]
da3.1_diagnostic_loci<-contrib3.1$var.names[contrib3.1$var.values>0.01]
da3.2_diagnostic_loci<-contrib3.2$var.names[contrib3.2$var.values>0.01]
daS.1_diagnostic_loci<-contribS.1$var.names[contribS.1$var.values>0.01]
daS.2_diagnostic_loci<-contribS.2$var.names[contribS.2$var.values>0.01]

all_diagnostic_loci<-unique(c(da1.1_diagnostic_loci, da1.2_diagnostic_loci, da2.1_diagnostic_loci, da2.2_diagnostic_loci, da3.1_diagnostic_loci, da3.2_diagnostic_loci, daS.1_diagnostic_loci, daS.2_diagnostic_loci))



#####Strata 1 DA 1 #########
SNP_names<-substr(da1.1_diagnostic_loci,1,nchar(da1.1_diagnostic_loci)-3)
freq_loci<-t(tab(genind2genpop(Strata1_genepop[loc=SNP_names]),freq=TRUE))
freq_loci<-as.data.frame(freq_loci[da1.1_diagnostic_loci,])
freq_loci$Locus<-rownames(freq_loci)
freq_loci<-gather(freq_loci,key="Population",value="Allele_Frequency",CHUK,EASTERN_BS,GOA)

theme_set(theme_bw()) 

da1.1_plot<-ggplot(data = freq_loci, aes(color=Locus,x=Population,y=Allele_Frequency,group=Locus)) +
  #geom_line(size = 1.2) +
  geom_jitter(size = 1.5,width = .15, height = 0) +
  labs(x="", y="")+
  ggtitle("Strata1 DA1")

#####Strata 1 DA 2 #########
SNP_names<-substr(da1.2_diagnostic_loci,1,nchar(da1.2_diagnostic_loci)-3)
freq_loci<-t(tab(genind2genpop(Strata1_genepop[loc=SNP_names]),freq=TRUE))
freq_loci<-as.data.frame(freq_loci[da1.2_diagnostic_loci,])
freq_loci$Locus<-rownames(freq_loci)
freq_loci<-gather(freq_loci,key="Population",value="Allele_Frequency",CHUK,EASTERN_BS,GOA)

theme_set(theme_bw()) 

da1.2_plot<-ggplot(data = freq_loci, aes(color=Locus,x=Population,y=Allele_Frequency,group=Locus)) +
  #geom_line(size = 1.2) +
  geom_jitter(size = 1.5,width = .15, height = 0) +
  labs(x="", y="")+
  ggtitle("Strata1 DA2")

#####Strata 2 DA 1 #########
SNP_names<-substr(da2.1_diagnostic_loci,1,nchar(da2.1_diagnostic_loci)-3)
freq_loci<-t(tab(genind2genpop(Strata2_genepop[loc=SNP_names]),freq=TRUE))
freq_loci<-as.data.frame(freq_loci[da2.1_diagnostic_loci,])
freq_loci$Locus<-rownames(freq_loci)
freq_loci<-gather(freq_loci,key="Population",value="Allele_Frequency",BAR,EBS,EGOA,WGOA)

theme_set(theme_bw()) 

da2.1_plot<-ggplot(data = freq_loci, aes(color=Locus,x=Population,y=Allele_Frequency,group=Locus)) +
  #geom_line(size = 1.2) +
  geom_jitter(size = 1.5,width = .15, height = 0) +
  labs(x="", y="")+
  ggtitle("Strata2 DA1")

#####Strata 2 DA 2 #########
SNP_names<-substr(da2.2_diagnostic_loci,1,nchar(da2.2_diagnostic_loci)-3)
freq_loci<-t(tab(genind2genpop(Strata2_genepop[loc=SNP_names]),freq=TRUE))
freq_loci<-as.data.frame(freq_loci[da2.2_diagnostic_loci,])
freq_loci$Locus<-rownames(freq_loci)
freq_loci<-gather(freq_loci,key="Population",value="Allele_Frequency",BAR,EBS,EGOA,WGOA)

theme_set(theme_bw()) 

da2.2_plot<-ggplot(data = freq_loci, aes(color=Locus,x=Population,y=Allele_Frequency,group=Locus)) +
  #geom_line(size = 1.2) +
  geom_jitter(size = 1.5,width = .15, height = 0) +
  labs(x="", y="")+
  ggtitle("Strata2 DA2")


#####Strata 3 DA 1 #########
SNP_names<-substr(da3.1_diagnostic_loci,1,nchar(da3.1_diagnostic_loci)-3)
freq_loci<-t(tab(genind2genpop(Strata3_genepop_filtered[loc=SNP_names]),freq=TRUE))
freq_loci<-as.data.frame(freq_loci[da3.1_diagnostic_loci,])
freq_loci$Locus<-rownames(freq_loci)
freq_loci<-gather(freq_loci,key="Population",value="Allele_Frequency",BARROW,COOK,COPPER,N_SEAK,NEBS)

theme_set(theme_bw()) 

da3.1_plot<-ggplot(data = freq_loci, aes(color=Locus,x=Population,y=Allele_Frequency,group=Locus)) +
  #geom_line(size = 1.2) +
  geom_jitter(size = 1.5,width = .15, height = 0) +
  labs(x="", y="")+
  ggtitle("Strata3 DA 1")

#####Strata 3 DA 2 #########
SNP_names<-substr(da3.2_diagnostic_loci,1,nchar(da3.2_diagnostic_loci)-3)
freq_loci<-t(tab(genind2genpop(Strata3_genepop_filtered[loc=SNP_names]),freq=TRUE))
freq_loci<-as.data.frame(freq_loci[da3.2_diagnostic_loci,])
freq_loci$Locus<-rownames(freq_loci)
freq_loci<-gather(freq_loci,key="Population",value="Allele_Frequency",BARROW,COOK,COPPER,N_SEAK,NEBS)

theme_set(theme_bw()) 

da3.2_plot<-ggplot(data = freq_loci, aes(color=Locus,x=Population,y=Allele_Frequency,group=Locus)) +
  #geom_line(size = 1.2) +
  geom_jitter(size = 1.5,width = .15, height = 0) +
  labs(x="", y="")+
  ggtitle("Strata3 DA 2")


#####South AK DA 1 #########
SNP_names<-substr(daS.1_diagnostic_loci,1,nchar(daS.1_diagnostic_loci)-3)
freq_loci<-t(tab(genind2genpop(South_AK_genepop[loc=SNP_names]),freq=TRUE))
freq_loci<-as.data.frame(freq_loci[daS.1_diagnostic_loci,])
freq_loci$Locus<-rownames(freq_loci)
freq_loci<-gather(freq_loci,key="Population",value="Allele_Frequency",COOK,COPPER,N_SEAK,NEBS)

theme_set(theme_bw()) 

daS.1_plot<-ggplot(data = freq_loci, aes(color=Locus,x=Population,y=Allele_Frequency,group=Locus)) +
  #geom_line(size = 1.2) +
  geom_jitter(size = 1.5,width = .15, height = 0) +
  labs(x="", y="")+
  ggtitle("South AK DA1")

#####South AK DA 2 #########
SNP_names<-substr(daS.2_diagnostic_loci,1,nchar(daS.2_diagnostic_loci)-3)
freq_loci<-t(tab(genind2genpop(South_AK_genepop[loc=SNP_names]),freq=TRUE))
freq_loci<-as.data.frame(freq_loci[daS.2_diagnostic_loci,])
freq_loci$Locus<-rownames(freq_loci)
freq_loci<-gather(freq_loci,key="Population",value="Allele_Frequency",COOK,COPPER,N_SEAK,NEBS)

theme_set(theme_bw()) 

daS.2_plot<-ggplot(data = freq_loci, aes(color=Locus,x=Population,y=Allele_Frequency,group=Locus)) +
  #geom_line(size = 1.2) +
  geom_jitter(size = 1.5,width = .15, height = 0) +
  labs(x="", y="")+
  ggtitle("South AK DA2")



Diagnostic_Loci_Plot<-ggarrange(ncol = 2, nrow=4,
                                da1.1_plot,da1.2_plot,
                                da2.1_plot,da2.2_plot,
                                da3.1_plot,da3.2_plot,
                                daS.1_plot,daS.2_plot)
Diagnostic_Loci_Plot


```


#Export workspace for use in relatedness/Ne/IBD script
```{r}

save.image(file="SNP_DAPC_Workspace.RData")

```


