---
title: "SNP_Porpoises_Rubias"
author: "Sam"
date: "7/17/2020"
output: pdf_document
---

*rubias* presents a series of intuitive analyses for assigning population of origin. They allow for power analyses to test the power of your marker set to assign population of origin. Here I analyze our SNP dataset, although rubias also allows for haplotype data. So, I will create an identical script for analyzing mtDNA data so we can compare.

It is almost certainly best to just use the populations with >5 samples. I could rank the loci by power and test the power of different subsets of loci (as I did in May et al 2020), but this would introduce high-grading bias via ranking or would require us to split the dataset, which we cannot afford to do. 

I'll use two primary functions here:

- A standard analysis in molecular ecology is to assign individuals in the reference back to the collections in the reference using a leave-one-out procedure. This is taken care of by the self_assign() function
-  To determine how much accuracy you can expect given a set of genetic markers and a grouping of populations (collections) into reporting units (repunits), assess_reference_loo() carries out simulations of mixtures using the leave-one-out approach of Anderson et al. (2008).


Requirements:
```{r, results="hide",warning=F,message=F}

library(tidyverse)
library(rubias)
library(ggpubr)
library(adegenet)

load("Relatedness_and_Fstats_Workspace.RData")

```

For naming consistency - changing names and removing pops with less than 5 samples

```{r}
popNames(Strata1_genepop)<-c("BARROW","E_BERING","GOA","W_BERING")
table(Strata1_genepop$pop)
Strata1_genepop<-Strata1_genepop[-which(Strata1_genepop$pop=="W_BERING")]

popNames(Strata2_genepop)<-c("BARROW","E_BERING","E_GOA","W_GOA","W_GOA","YAKUTAT")
table(Strata2_genepop$pop)
Strata2_genepop<-Strata2_genepop[-which(Strata2_genepop$pop=="YAKUTAT")]

popNames(Strata3_genepop)<-c("BARROW","COOK","COPPER","N_SEAK","NE_BERING","S_SEAK","SE_BERING","W_BERING","YAKUTAT")
table(Strata3_genepop$pop)
Strata3_genepop<-Strata3_genepop[-which(Strata3_genepop$pop%in%c("SE_BERING","S_SEAK","W_BERING","YAKUTAT"))]


```

Data:

Rubias has a specific format:

- sample_type 
- repunit 
- collection 
- indiv
- 2 columns per locus

### Repunit-Collection Site Comparisons

In the following code blocks, the repunit is the strata unit and the collection is the strata 3 collection site. I'll perform first assess_reference_loo to simulate individuals and assess the power to assign each collection site to its strata unit. The shorthand for this repunit-collection site comparison is either repu-col or RC

```{r,warning=F,message=F}
###Strata1
table(Strata1_genepop$pop)
Strata1_df<-genind2df(Strata1_genepop,oneColPerAll = T)

Strata1_reference<-data.frame(sample_type=rep("reference", nrow(Strata1_df)), 
           repunit=Strata1_df$pop,
           collection=Strata1_genepop$other$Strata3,
           indiv=rownames(Strata1_df))
Strata1_reference<-cbind(Strata1_reference,Strata1_df[,2:ncol(Strata1_df)])

Strata1_reference$repunit<-as.character(Strata1_reference$repunit)
Strata1_reference$collection<-as.character(Strata1_reference$collection)
Strata1_reference$indiv<-as.character(Strata1_reference$indiv)

###Strata2
table(Strata2_genepop$pop)
Strata2_df<-genind2df(Strata2_genepop,oneColPerAll = T)

Strata2_reference<-data.frame(sample_type=rep("reference", nrow(Strata2_df)), 
           repunit=Strata2_df$pop,
           collection=Strata2_genepop$other$Strata3,
           indiv=rownames(Strata2_df))
Strata2_reference<-cbind(Strata2_reference,Strata2_df[,2:ncol(Strata2_df)])

Strata2_reference$repunit<-as.character(Strata2_reference$repunit)
Strata2_reference$collection<-as.character(Strata2_reference$collection)
Strata2_reference$indiv<-as.character(Strata2_reference$indiv)

###Strata3
table(Strata3_genepop$pop)
Strata3_df<-genind2df(Strata3_genepop,oneColPerAll = T)

Strata3_reference<-data.frame(sample_type=rep("reference", nrow(Strata3_df)), 
           repunit=Strata3_df$pop,
           collection=Strata3_genepop$other$Strata3,
           indiv=rownames(Strata3_df))
Strata3_reference<-cbind(Strata3_reference,Strata3_df[,2:ncol(Strata3_df)])

Strata3_reference$repunit<-as.character(Strata3_reference$repunit)
Strata3_reference$collection<-as.character(Strata3_reference$collection)
Strata3_reference$indiv<-as.character(Strata3_reference$indiv)

#GOA:
table(Strata3_genepop$pop)
GOA_genepop<-Strata3_genepop[which(Strata3_genepop$other$Strata3%in%c("COOK","COPPER","N_SEAK","S_SEAK","YAKUTAT"))]
GOA_df<-genind2df(GOA_genepop,oneColPerAll = T)

GOA_reference<-data.frame(sample_type=rep("reference", nrow(GOA_df)), 
           repunit=GOA_genepop$other$Strata3,
           collection=GOA_genepop$other$Strata3,
           indiv=rownames(GOA_df))
GOA_reference<-cbind(GOA_reference,GOA_df[,2:ncol(GOA_df)])

GOA_reference$repunit<-as.character(GOA_reference$repunit)
GOA_reference$collection<-as.character(GOA_reference$collection)
GOA_reference$indiv<-as.character(GOA_reference$indiv)

#GOA_filtered:
GOA_genepop_filtered<-Strata3_genepop[which(Strata3_genepop$other$Strata3%in%c("COOK","COPPER","N_SEAK"))]
GOA_df_filtered<-genind2df(GOA_genepop_filtered,oneColPerAll = T)

GOA_reference_filtered<-data.frame(sample_type=rep("reference", nrow(GOA_df_filtered)), 
           repunit=GOA_genepop_filtered$other$Strata3,
           collection=GOA_genepop_filtered$other$Strata3,
           indiv=rownames(GOA_df_filtered))
GOA_reference_filtered<-cbind(GOA_reference_filtered,GOA_df_filtered[,2:ncol(GOA_df_filtered)])

GOA_reference_filtered$repunit<-as.character(GOA_reference_filtered$repunit)
GOA_reference_filtered$collection<-as.character(GOA_reference_filtered$collection)
GOA_reference_filtered$indiv<-as.character(GOA_reference_filtered$indiv)



```


Assess reference loo: Strata 1
```{r, warning=F,message=F}
ppho_sims <- assess_reference_loo(reference = Strata1_reference, 
                     gen_start_col = 5, 
                     reps = 1000, 
                     mixsize = 1000,
                     return_indiv_posteriors = T,
                     resampling_unit = "individual")

# summarise things
repu_pofzs <- ppho_sims$indiv_posteriors %>%
  filter(repunit == simulated_repunit) %>%
  group_by(iter, indiv, simulated_collection, repunit) %>%  # first aggregate over reporting units
  summarise(repu_PofZ = sum(PofZ)) %>%
  ungroup() %>%
  arrange(repunit, simulated_collection) %>%
  mutate(simulated_collection = factor(simulated_collection, levels = unique(simulated_collection)))

# also get the number of simulated individuals from each collection
num_simmed <- ppho_sims$indiv_posteriors %>%
  group_by(iter, indiv) %>%
  slice(1) %>%
  ungroup() %>%
  count(simulated_collection)
  
# note, the last few steps make simulated collection a factor so that collections within
# the same repunit are grouped together in the plot.

# now, plot it
arl_RC_gg1<-ggplot(repu_pofzs, aes(x = simulated_collection, y = repu_PofZ)) +
  geom_boxplot(aes(colour = repunit)) +
  geom_text(data = num_simmed, mapping = aes(y = 1.025, label = n), angle = 90, hjust = 0, vjust = 0.5, size = 3) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 9, vjust = 0.5)) +
  ylim(c(NA, 1.05)) +
  ggtitle("Strata1 Simulated Assignments RC")

```


### Assess reference loo: Strata 2
```{r, warning=F,message=F}
Strata2_sims <- assess_reference_loo(reference = Strata2_reference, 
                     gen_start_col = 5, 
                     reps = 1000, 
                     mixsize = 1000,
                     return_indiv_posteriors = T,
                     resampling_unit = "individual")

# summarise things
repu_pofzs <- Strata2_sims$indiv_posteriors %>%
  filter(repunit == simulated_repunit) %>%
  group_by(iter, indiv, simulated_collection, repunit) %>%  # first aggregate over reporting units
  summarise(repu_PofZ = sum(PofZ)) %>%
  ungroup() %>%
  arrange(repunit, simulated_collection) %>%
  mutate(simulated_collection = factor(simulated_collection, levels = unique(simulated_collection)))

# also get the number of simulated individuals from each collection
num_simmed <- Strata2_sims$indiv_posteriors %>%
  group_by(iter, indiv) %>%
  slice(1) %>%
  ungroup() %>%
  count(simulated_collection)
  
# note, the last few steps make simulated collection a factor so that collections within
# the same repunit are grouped together in the plot.

# now, plot it
arl_RC_gg2<-ggplot(repu_pofzs, aes(x = simulated_collection, y = repu_PofZ)) +
  geom_boxplot(aes(colour = repunit)) +
  geom_text(data = num_simmed, mapping = aes(y = 1.025, label = n), angle = 90, hjust = 0, vjust = 0.5, size = 3) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 9, vjust = 0.5)) +
  ylim(c(NA, 1.05)) +
  ggtitle("Strata2 Simulated Assignments RC")


```


### Assess reference loo: Strata 3

```{r, warning=F,message=F}
Strata3_reference$collection[which(Strata3_reference$collection=="NEBS")]<-"NE_BERING"

Strata3_sims_snps <- assess_reference_loo(reference = Strata3_reference, 
                     gen_start_col = 5, 
                     reps = 1000, 
                     mixsize = 1000,
                     return_indiv_posteriors = T,
                     resampling_unit = "gene_copies")

# summarise things
repu_pofzs_snps <- Strata3_sims_snps$indiv_posteriors %>%
  filter(repunit == simulated_repunit) %>%
  group_by(iter, indiv, simulated_collection, repunit) %>%  # first aggregate over reporting units
  summarise(repu_PofZ = sum(PofZ)) %>%
  ungroup() %>%
  arrange(repunit, simulated_collection) %>%
  mutate(simulated_collection = factor(simulated_collection, levels = unique(simulated_collection)))
repu_pofzs_snps$type<-"SNPs"

# also get the number of simulated individuals from each collection
num_simmed <- Strata3_sims_snps$indiv_posteriors %>%
  group_by(iter, indiv) %>%
  slice(1) %>%
  ungroup() %>%
  count(simulated_collection)
  
# note, the last few steps make simulated collection a factor so that collections within
# the same repunit are grouped together in the plot.

# now, plot it
arl_RC_gg3_snps<- ggplot(repu_pofzs_snps, aes(x = simulated_collection, y = repu_PofZ)) +
  geom_boxplot(aes(colour = repunit)) +
  #geom_text(data = num_simmed, mapping = aes(y = 1.025, label = n), angle = 90, hjust = 0, vjust = 0.5, size = 3) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 9, vjust = 0.5),
        legend.position = "none") +
  ylim(c(NA, 1.05))+
  ggtitle("SNPs")+
  xlab("Collection Site")+
  ylab("Assignment Probability")
arl_RC_gg3_snps

repu_pofzs_snps%>%group_by(simulated_collection)%>%summarize(mean=mean(repu_PofZ),sd=sd(repu_PofZ))

```

### Assess reference loo: GOA

```{r, warning=F,message=F}
GOA_sims <- assess_reference_loo(reference = GOA_reference, 
                     gen_start_col = 5, 
                     reps = 1000, 
                     mixsize = 1000,
                     return_indiv_posteriors = T,
                     resampling_unit = "individual")

# summarise things
repu_pofzs <- GOA_sims$indiv_posteriors %>%
  filter(repunit == simulated_repunit) %>%
  group_by(iter, indiv, simulated_collection, repunit) %>%  # first aggregate over reporting units
  summarise(repu_PofZ = sum(PofZ)) %>%
  ungroup() %>%
  arrange(repunit, simulated_collection) %>%
  mutate(simulated_collection = factor(simulated_collection, levels = unique(simulated_collection)))

# also get the number of simulated individuals from each collection
num_simmed <- GOA_sims$indiv_posteriors %>%
  group_by(iter, indiv) %>%
  slice(1) %>%
  ungroup() %>%
  count(simulated_collection)
  
# note, the last few steps make simulated collection a factor so that collections within
# the same repunit are grouped together in the plot.

# now, plot it
arl_RC_gg_goa<- ggplot(repu_pofzs, aes(x = simulated_collection, y = repu_PofZ)) +
  geom_boxplot(aes(colour = repunit)) +
  geom_text(data = num_simmed, mapping = aes(y = 1.025, label = n), angle = 90, hjust = 0, vjust = 0.5, size = 3) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 9, vjust = 0.5)) +
  ylim(c(NA, 1.05))+
  ggtitle("GOA Simulated Assignments RC")

```

### Assess reference loo: GOA_filtered

```{r, warning=F,message=F}
GOA_sims <- assess_reference_loo(reference = GOA_reference_filtered, 
                     gen_start_col = 5, 
                     reps = 1000, 
                     mixsize = 1000,
                     return_indiv_posteriors = T,
                     resampling_unit = "individual")

# summarise things
repu_pofzs <- GOA_sims$indiv_posteriors %>%
  filter(repunit == simulated_repunit) %>%
  group_by(iter, indiv, simulated_collection, repunit) %>%  # first aggregate over reporting units
  summarise(repu_PofZ = sum(PofZ)) %>%
  ungroup() %>%
  arrange(repunit, simulated_collection) %>%
  mutate(simulated_collection = factor(simulated_collection, levels = unique(simulated_collection)))

# also get the number of simulated individuals from each collection
num_simmed <- GOA_sims$indiv_posteriors %>%
  group_by(iter, indiv) %>%
  slice(1) %>%
  ungroup() %>%
  count(simulated_collection)
  
# note, the last few steps make simulated collection a factor so that collections within
# the same repunit are grouped together in the plot.

# now, plot it
arl_RC_gg_goa_filtered<- ggplot(repu_pofzs, aes(x = simulated_collection, y = repu_PofZ)) +
  geom_boxplot(aes(colour = repunit)) +
  geom_text(data = num_simmed, mapping = aes(y = 1.025, label = n), angle = 90, hjust = 0, vjust = 0.5, size = 3) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 9, vjust = 0.5)) +
  ylim(c(NA, 1.05))+
  ggtitle("GOA Simulated Assignments RC")

```


ggarrange assess reference loo plots:

```{r,warning=F,message=F}
arl_RC_all<-ggarrange(arl_RC_gg1,arl_RC_gg2,arl_RC_gg3,ncol = 1)
arl_RC_all

```


Self Assign:
```{r,warning=F,message=F}

###Strata 1
sa_strata1 <- self_assign(reference = Strata1_reference, gen_start_col = 5)

sa_to_repu_1 <- sa_strata1 %>%
  group_by(indiv, collection, repunit, inferred_repunit) %>%
  summarise(repu_scaled_like = sum(scaled_likelihood)) %>%
  filter(repunit==inferred_repunit) # just take the rows where repunit = inferred repunit

sa_strata1 %>% group_by(repunit) %>% 
  filter(repunit==inferred_repunit)%>%
  summarise(mean=mean(scaled_likelihood))

sa_RC_gg1<- sa_to_repu_1 %>% ggplot(aes(y=repu_scaled_like,x=repunit)) +
  geom_boxplot() +
  ggtitle("Strata1 Self-Assign RC")

###Strata 2
sa_strata2 <- self_assign(reference = Strata2_reference, gen_start_col = 5)

sa_to_repu_2 <- sa_strata2 %>%
  group_by(indiv, collection, repunit, inferred_repunit) %>%
  summarise(repu_scaled_like = sum(scaled_likelihood)) %>%
  filter(repunit==inferred_repunit) # just take the rows where repunit = inferred repunit

sa_RC_gg2 <-sa_to_repu_2 %>% ggplot(aes(y=repu_scaled_like,x=repunit)) +
  geom_boxplot() +
  ggtitle("Strata2 Self-Assign RC")

#Strata 3
sa_strata3 <- self_assign(reference = Strata3_reference, gen_start_col = 5)

sa_to_repu_3 <- sa_strata3 %>%
  group_by(indiv, collection, repunit, inferred_repunit) %>%
  summarise(repu_scaled_like = sum(scaled_likelihood)) %>%
  filter(repunit==inferred_repunit) # just take the rows where repunit = inferred repunit

sa_RC_gg3<- sa_to_repu_3 %>% ggplot(aes(y=repu_scaled_like,x=repunit)) +
  geom_boxplot() +
  ggtitle("Strata3 Self-Assign RC")

sa_RC_all<-ggarrange(sa_RC_gg1,sa_RC_gg2,sa_RC_gg3,ncol = 1)
sa_RC_all
```

GOA Self Assign:
```{r}
sa_goa <- self_assign(reference = GOA_reference, gen_start_col = 5)

sa_to_repu_goa <- sa_goa %>%
  group_by(indiv, collection, repunit, inferred_repunit) %>%
  summarise(repu_scaled_like = sum(scaled_likelihood)) %>%
  filter(repunit==inferred_repunit) # just take the rows where repunit = inferred repunit

sa_RC_gg_goa<- sa_to_repu_goa %>% ggplot(aes(y=repu_scaled_like,x=repunit)) +
  geom_boxplot() +
  ggtitle("GOA Self-Assign RC")

sa_goa_f <- self_assign(reference = GOA_reference_filtered, gen_start_col = 5)

sa_to_repu_goa <- sa_goa_f %>%
  group_by(indiv, collection, repunit, inferred_repunit) %>%
  summarise(repu_scaled_like = sum(scaled_likelihood)) %>%
  filter(repunit==inferred_repunit) # just take the rows where repunit = inferred repunit

sa_RC_gg_goa_filtered<- sa_to_repu_goa %>% ggplot(aes(y=repu_scaled_like,x=repunit)) +
  geom_boxplot() +
  ggtitle("GOA_filtered Self-Assign RC")



sa_RC_goa<-ggarrange(sa_RC_gg_goa,sa_RC_gg_goa_filtered,arl_RC_gg_goa,arl_RC_gg_goa_filtered)
sa_RC_goa


```



### Repunit-Repunit Comparisons

In the following code blocks, the repunit is the strata unit and the collection is also the strata unit, not the collection site. I'll perform first assess_reference_loo to simulate individuals and assess the power to assign each collection site to its strata unit. The shorthand for this repunit-repunit comparison is either repu-repu or RR

```{r,warning=F,message=F}
###Strata1
table(Strata1_genepop$pop)
Strata1_df<-genind2df(Strata1_genepop,oneColPerAll = T)

Strata1_reference<-data.frame(sample_type=rep("reference", nrow(Strata1_df)), 
           repunit=Strata1_df$pop,
           collection=Strata1_df$pop,
           indiv=rownames(Strata1_df))
Strata1_reference<-cbind(Strata1_reference,Strata1_df[,2:ncol(Strata1_df)])

Strata1_reference$repunit<-as.character(Strata1_reference$repunit)
Strata1_reference$collection<-as.character(Strata1_reference$collection)
Strata1_reference$indiv<-as.character(Strata1_reference$indiv)

###Strata2
table(Strata2_genepop$pop)
Strata2_df<-genind2df(Strata2_genepop,oneColPerAll = T)

Strata2_reference<-data.frame(sample_type=rep("reference", nrow(Strata2_df)), 
           repunit=Strata2_df$pop,
           collection=Strata2_df$pop,
           indiv=rownames(Strata2_df))
Strata2_reference<-cbind(Strata2_reference,Strata2_df[,2:ncol(Strata2_df)])

Strata2_reference$repunit<-as.character(Strata2_reference$repunit)
Strata2_reference$collection<-as.character(Strata2_reference$collection)
Strata2_reference$indiv<-as.character(Strata2_reference$indiv)

###Strata3
table(Strata3_genepop_filtered$pop)
Strata3_df<-genind2df(Strata3_genepop_filtered,oneColPerAll = T)

Strata3_reference<-data.frame(sample_type=rep("reference", nrow(Strata3_df)), 
           repunit=Strata3_df$pop,
           collection=Strata3_df$pop,
           indiv=rownames(Strata3_df))
Strata3_reference<-cbind(Strata3_reference,Strata3_df[,2:ncol(Strata3_df)])

Strata3_reference$repunit<-as.character(Strata3_reference$repunit)
Strata3_reference$collection<-as.character(Strata3_reference$collection)
Strata3_reference$indiv<-as.character(Strata3_reference$indiv)
```


Assess reference loo: Strata 1
```{r,warning=F,message=F}
ppho_sims <- assess_reference_loo(reference = Strata1_reference, 
                     gen_start_col = 5, 
                     reps = 1000, 
                     mixsize = 1000,
                     return_indiv_posteriors = T,
                     resampling_unit = "individual")

# summarise things
repu_pofzs <- ppho_sims$indiv_posteriors %>%
  filter(repunit == simulated_repunit) %>%
  group_by(iter, indiv, simulated_collection, repunit) %>%  # first aggregate over reporting units
  summarise(repu_PofZ = sum(PofZ)) %>%
  ungroup() %>%
  arrange(repunit, simulated_collection) %>%
  mutate(simulated_collection = factor(simulated_collection, levels = unique(simulated_collection)))

# also get the number of simulated individuals from each collection
num_simmed <- ppho_sims$indiv_posteriors %>%
  group_by(iter, indiv) %>%
  slice(1) %>%
  ungroup() %>%
  count(simulated_collection)
  
# note, the last few steps make simulated collection a factor so that collections within
# the same repunit are grouped together in the plot.

# now, plot it
arl_RR_gg1<-ggplot(repu_pofzs, aes(x = simulated_collection, y = repu_PofZ)) +
  geom_boxplot(aes(colour = repunit)) +
  geom_text(data = num_simmed, mapping = aes(y = 1.025, label = n), angle = 90, hjust = 0, vjust = 0.5, size = 3) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 9, vjust = 0.5)) +
  ylim(c(NA, 1.05)) +
  ggtitle("Strata1 Simulated Assignments RR")

repu_pofzs%>%group_by(repunit)%>%summarise(mean=mean(repu_PofZ),sd=sd(repu_PofZ))

```


### Assess reference loo: Strata 2
```{r,warning=F,message=F}
Strata2_sims <- assess_reference_loo(reference = Strata2_reference, 
                     gen_start_col = 5, 
                     reps = 1000, 
                     mixsize = 1000,
                     return_indiv_posteriors = T,
                     resampling_unit = "individual")

# summarise things
repu_pofzs <- Strata2_sims$indiv_posteriors %>%
  filter(repunit == simulated_repunit) %>%
  group_by(iter, indiv, simulated_collection, repunit) %>%  # first aggregate over reporting units
  summarise(repu_PofZ = sum(PofZ)) %>%
  ungroup() %>%
  arrange(repunit, simulated_collection) %>%
  mutate(simulated_collection = factor(simulated_collection, levels = unique(simulated_collection)))

# also get the number of simulated individuals from each collection
num_simmed <- Strata2_sims$indiv_posteriors %>%
  group_by(iter, indiv) %>%
  slice(1) %>%
  ungroup() %>%
  count(simulated_collection)
  
# note, the last few steps make simulated collection a factor so that collections within
# the same repunit are grouped together in the plot.

# now, plot it
arl_RR_gg2<-ggplot(repu_pofzs, aes(x = simulated_collection, y = repu_PofZ)) +
  geom_boxplot(aes(colour = repunit)) +
  geom_text(data = num_simmed, mapping = aes(y = 1.025, label = n), angle = 90, hjust = 0, vjust = 0.5, size = 3) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 9, vjust = 0.5)) +
  ylim(c(NA, 1.05)) +
  ggtitle("Strata2 Simulated Assignments RR")


```


### Assess reference loo: Strata 3

```{r,warning=F,message=F}
Strata3_sims <- assess_reference_loo(reference = Strata3_reference, 
                     gen_start_col = 5, 
                     reps = 1000, 
                     mixsize = 1000,
                     return_indiv_posteriors = T,
                     resampling_unit = "individual")

# summarise things
repu_pofzs <- Strata3_sims$indiv_posteriors %>%
  filter(repunit == simulated_repunit) %>%
  group_by(iter, indiv, simulated_collection, repunit) %>%  # first aggregate over reporting units
  summarise(repu_PofZ = sum(PofZ)) %>%
  ungroup() %>%
  arrange(repunit, simulated_collection) %>%
  mutate(simulated_collection = factor(simulated_collection, levels = unique(simulated_collection)))

# also get the number of simulated individuals from each collection
num_simmed <- Strata3_sims$indiv_posteriors %>%
  group_by(iter, indiv) %>%
  slice(1) %>%
  ungroup() %>%
  count(simulated_collection)
  
# note, the last few steps make simulated collection a factor so that collections within
# the same repunit are grouped together in the plot.

# now, plot it
arl_RR_gg3<- ggplot(repu_pofzs, aes(x = simulated_collection, y = repu_PofZ)) +
  geom_boxplot(aes(colour = repunit)) +
  geom_text(data = num_simmed, mapping = aes(y = 1.025, label = n), angle = 90, hjust = 0, vjust = 0.5, size = 3) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 9, vjust = 0.5)) +
  ylim(c(NA, 1.05))+
  ggtitle("Strata3 Simulated Assignments RR")

```

ggarrange assess reference loo plots:

```{r,warning=F,message=F}
arl_RR_all<-ggarrange(arl_RR_gg1,arl_RR_gg2,arl_RR_gg3,ncol = 1)
arl_RR_all
```


Self Assign:
```{r,warning=F,message=F}

###Strata 1
sa_strata1 <- self_assign(reference = Strata1_reference, gen_start_col = 5)

sa_to_repu_1 <- sa_strata1 %>%
  group_by(indiv, collection, repunit, inferred_repunit) %>%
  summarise(repu_scaled_like = sum(scaled_likelihood)) %>%
  filter(repunit==inferred_repunit) # just take the rows where repunit = inferred repunit

sa_RR_gg1<- sa_to_repu_1 %>% ggplot(aes(y=repu_scaled_like,x=repunit)) +
  geom_boxplot() +
  ggtitle("Strata1 Self-Assign RR")

###Strata 2
sa_strata2 <- self_assign(reference = Strata2_reference, gen_start_col = 5)

sa_to_repu_2 <- sa_strata2 %>%
  group_by(indiv, collection, repunit, inferred_repunit) %>%
  summarise(repu_scaled_like = sum(scaled_likelihood)) %>%
  filter(repunit==inferred_repunit) # just take the rows where repunit = inferred repunit

sa_RR_gg2 <-sa_to_repu_2 %>% ggplot(aes(y=repu_scaled_like,x=repunit)) +
  geom_boxplot() +
  ggtitle("Strata2 Self-Assign RR")

#Strata 3
sa_strata3 <- self_assign(reference = Strata3_reference, gen_start_col = 5)

sa_to_repu_3 <- sa_strata3 %>%
  group_by(indiv, collection, repunit, inferred_repunit) %>%
  summarise(repu_scaled_like = sum(scaled_likelihood)) %>%
  filter(repunit==inferred_repunit) # just take the rows where repunit = inferred repunit

sa_RR_gg3<- sa_to_repu_3 %>% ggplot(aes(y=repu_scaled_like,x=repunit)) +
  geom_boxplot() +
  ggtitle("Strata3 Self-Assign RR")

sa_RR_all<-ggarrange(sa_RR_gg1,sa_RR_gg2,sa_RR_gg3,ncol = 1)
sa_RR_all

```

Final figures:

```{r,warning=F,message=F}
arl_plot<-ggarrange(arl_RC_all,arl_RR_all,ncol = 2)
arl_plot
  
sa_RR_all

```