---
title: "SNP_PCAs_and_sPCAs"
author: "Sam May"
date: "August 29, 2020"
output: pdf_document
---


PCAs and sPCAs for harbor porposes - loading data from DACP script. 

Note, PCAs require no missing data - will be imputed using population medians. Low missing data means this shouldn't have a large homogenizing effect, but it still may. 

```{r}
load("SNP_DAPC_Workspace.RData")

library(viridis)
library(adegenet)
library(strataG)
library(spdep)
library(tidyverse)
library(gtools)
library(PBSmapping)
library(maps)
library(ggplot2)
library(rworldmap)
library(swfscMisc)
library(fields)
library(RColorBrewer)
library(mapplots)
library(marmap)
library(raster)
library(splancs)

```

###Regular PCAs first:

#Strata 1:

```{r}

Strata1_genepop<-AK_genepop
Strata1_genepop$pop<-as.factor(Strata1_genepop$other$Strata1)
#Strata1_genepop<-Strata1_genepop[!Strata1_genepop$pop=="KODIAK"]

Strata1_scaled <- scaleGen(Strata1_genepop, NA.method="mean")

Strata1_PCA<-dudi.pca(Strata1_scaled,cent=T,scale=F,scannf=F,nf=3) #Run PCA
Strata1_PCA_df<- Strata1_PCA$li #save coordniates in a data frame
Strata1_PCA_df$pop<-Strata1_genepop$pop #add individual populations to data frame

Strata1_PCA_df$pop<-factor(Strata1_PCA_df$pop,levels=c("CHUK","EASTERN_BS","GOA","WESTERN_BS"))
Strata1_pop_colors<-viridis(4)

# get percent var explained per axis / principal component, for plot
PC_eigs_out <- Strata1_PCA$eig
PC_axis1_var_out <- paste(substr(as.character((PC_eigs_out[1] / sum(PC_eigs_out))*100),1,5),"%",sep="")
PC_axis2_var_out <- paste(substr(as.character((PC_eigs_out[2] / sum(PC_eigs_out))*100),1,5),"%",sep="")

Strata1_PCA_plot <- ggplot(data = Strata1_PCA_df, aes(x= Axis1, y= Axis2)) + 
  geom_point(aes(colour = pop), size = 3.0, alpha = 0.7) +
  scale_colour_manual(values=Strata1_pop_colors) +
  #geom_text(aes(label=rownames(AK_Collection_PCA_df)),nudge_x=5,nudge_y = 5)+
  theme(plot.margin = unit(c(6,0,6,0), "pt")) +
  labs(x=paste("PC1",PC_axis1_var_out), y=paste("PC2", PC_axis2_var_out)) +
  ggtitle("Strata 1")+
  theme_classic() +
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank(),
        axis.text.y=element_blank(), axis.ticks.y=element_blank()) +
  theme(legend.position="right") +
  theme(legend.title=element_blank())
Strata1_PCA_plot

```

```{r}

Strata2_genepop<-AK_genepop
Strata2_genepop$pop<-as.factor(Strata2_genepop$other$Strata2)
Strata2_genepop<-Strata2_genepop[!Strata3_genepop$pop=="KODIAK"]

Strata2_scaled <- scaleGen(Strata2_genepop, NA.method="mean")

Strata2_PCA<-dudi.pca(Strata2_scaled,cent=T,scale=F,scannf=F,nf=3) #Run PCA
Strata2_PCA_df<- Strata2_PCA$li #save coordniates in a data frame
Strata2_PCA_df$pop<-Strata2_genepop$pop #add individual populations to data frame

Strata2_PCA_df$pop<-factor(Strata2_PCA_df$pop,levels=c("BAR","EBS","WBS","WGOA","YAKUTAT","EGOA"))
Strata2_pop_colors<-viridis(6)

# get percent var explained per axis / principal component, for plot
PC_eigs_out <- Strata2_PCA$eig
PC_axis1_var_out <- paste(substr(as.character((PC_eigs_out[1] / sum(PC_eigs_out))*100),1,5),"%",sep="")
PC_axis2_var_out <- paste(substr(as.character((PC_eigs_out[2] / sum(PC_eigs_out))*100),1,5),"%",sep="")

Strata2_PCA_plot <- ggplot(data = Strata2_PCA_df, aes(x= Axis1, y= Axis2)) + 
  geom_point(aes(colour = pop), size = 3.0, alpha = 0.7) +
  scale_colour_manual(values=Strata2_pop_colors) +
  #geom_text(aes(label=rownames(AK_Collection_PCA_df)),nudge_x=5,nudge_y = 5)+
  theme(plot.margin = unit(c(6,0,6,0), "pt")) +
  labs(x=paste("PC1",PC_axis1_var_out), y=paste("PC2", PC_axis2_var_out)) +
  ggtitle("Strata 2")+
  theme_classic() +
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank(),
        axis.text.y=element_blank(), axis.ticks.y=element_blank()) +
  theme(legend.position="right") +
  theme(legend.title=element_blank())
Strata2_PCA_plot

```

```{r}

Strata3_genepop<-AK_genepop
Strata3_genepop$pop<-as.factor(Strata3_genepop$other$Strata3)
Strata3_genepop<-Strata3_genepop[!Strata3_genepop$pop=="KODIAK"]

Strata3_scaled <- scaleGen(Strata3_genepop, NA.method="mean")

Strata3_PCA<-dudi.pca(Strata3_scaled,cent=T,scale=F,scannf=F,nf=3) #Run PCA
Strata3_PCA_df<- Strata3_PCA$li #save coordniates in a data frame
Strata3_PCA_df$pop<-Strata3_genepop$pop #add individual populations to data frame

Strata3_PCA_df$pop<-factor(Strata3_PCA_df$pop,levels=c("BARROW","WBS","NEBS","SEBS","COOK","COPPER","YAKUTAT","N_SEAK","S_SEAK"))
Strata3_pop_colors<-c("yellow","orange","black","hotpink","pink","green","gold","blue","purple")

# get percent var explained per axis / principal component, for plot
PC_eigs_out <- Strata3_PCA$eig
PC_axis1_var_out <- paste(substr(as.character((PC_eigs_out[1] / sum(PC_eigs_out))*100),1,5),"%",sep="")
PC_axis2_var_out <- paste(substr(as.character((PC_eigs_out[2] / sum(PC_eigs_out))*100),1,5),"%",sep="")

Strata3_PCA_plot <- ggplot(data = Strata3_PCA_df, aes(x= Axis1, y= Axis2)) + 
  geom_point(aes(colour = pop), size = 3.0, alpha = 0.7) +
  scale_colour_manual(values=Strata3_pop_colors) +
  #geom_text(aes(label=rownames(AK_Collection_PCA_df)),nudge_x=5,nudge_y = 5)+
  theme(plot.margin = unit(c(6,0,6,0), "pt")) +
  labs(x=paste("PC1",PC_axis1_var_out), y=paste("PC2", PC_axis2_var_out)) +
  ggtitle("Strata 3")+
  theme_classic() +
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank(),
        axis.text.y=element_blank(), axis.ticks.y=element_blank()) +
  theme(legend.position="right") +
  theme(legend.title=element_blank())
Strata3_PCA_plot

```

South AK Large Pops
```{r}

SAK_genepop<-AK_genepop
SAK_genepop$pop<-as.factor(SAK_genepop$other$Strata3)
SAK_genepop<-SAK_genepop[!SAK_genepop$pop%in%c("KODIAK","WBS","SEBS","BARROW","YAKUTAT","S_SEAK")]

SAK_scaled <- scaleGen(SAK_genepop, NA.method="mean")

SAK_PCA<-dudi.pca(SAK_scaled,cent=T,scale=F,scannf=F,nf=3) #Run PCA
SAK_PCA_df<- SAK_PCA$li #save coordniates in a data frame
SAK_PCA_df$pop<-SAK_genepop$pop #add individual populations to data frame

SAK_PCA_df$pop<-factor(SAK_PCA_df$pop,levels=c("NEBS","COOK","COPPER","N_SEAK"))
SAK_pop_colors<-c("black","pink","green","blue")

# get percent var explained per axis / principal component, for plot
PC_eigs_out <- SAK_PCA$eig
PC_axis1_var_out <- paste(substr(as.character((PC_eigs_out[1] / sum(PC_eigs_out))*100),1,5),"%",sep="")
PC_axis2_var_out <- paste(substr(as.character((PC_eigs_out[2] / sum(PC_eigs_out))*100),1,5),"%",sep="")

SAK_PCA_plot <- ggplot(data = SAK_PCA_df, aes(x= Axis1, y= Axis2)) + 
  geom_point(aes(colour = pop), size = 3.0, alpha = 0.7) +
  scale_colour_manual(values=SAK_pop_colors) +
  #geom_text(aes(label=rownames(AK_Collection_PCA_df)),nudge_x=5,nudge_y = 5)+
  theme(plot.margin = unit(c(6,0,6,0), "pt")) +
  labs(x=paste("PC1",PC_axis1_var_out), y=paste("PC2", PC_axis2_var_out)) +
  ggtitle("Strata 3, n>10")+
  theme_classic() +
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank(),
        axis.text.y=element_blank(), axis.ticks.y=element_blank()) +
  theme(legend.position="right") +
  theme(legend.title=element_blank())
SAK_PCA_plot

```

```{r}
ggarrange(Strata1_PCA_plot,Strata2_PCA_plot,Strata3_PCA_plot,SAK_PCA_plot)


```

So, PCAs clearly show no structure ... what if we add in geographic information?
Code mostly from P.Morin

```{r}
title="Strata1"

Strata1_genepop$other$xy$x<-as.numeric(Strata1_genepop$other$xy$x)
Strata1_genepop$other$xy$y<-as.numeric(Strata1_genepop$other$xy$y)

Strata1_genepop$other$xy$x<-jitter(Strata1_genepop$other$xy$x, factor = .5)
Strata1_genepop$other$xy$y<-jitter(Strata1_genepop$other$xy$y, factor = .5)

#NAs are automatically replaced to mean allele frequency:
mySpca <- spca(Strata1_genepop, ask=T, type=1, scannf=F, nfposi = 4, nfnega = 0, scale=T) # method used by LL


# Positive eigenvalues (on the left) correspond to global structures, while negative eigenvalues (on the right) indicate local patterns.
barplot(mySpca$eig, main="sPCA eigenvalues",
col=spectral(length(mySpca$eig)))
legend("topright", fill=spectral(2),
leg=c("Global structures", "Local structures"))
abline(h=0,col="grey")

sp <- screeplot(mySpca,main = "Strata1 Spatial and Variance Components of the Eigenvalues")

# WHEN THIS DOESN'T WORK, it's because the number of eigenvectors doesn't match the number of expected (?) eigenvectors. For 88 samples, there should be 87 eigenvectors, so if mySpca$eig = anything other than 87, there will be an error. The only way I've found to fix this is to change the factor parameter when the lat/lon positions are jittered, then re-run sPCA.
# Re-running it over and over again with the same factor can also result in different numbers of eigenvalues, so you can just re-run this section until it works.

```

spatial and variance components of the eigenvalues (tutorial p. 13-14)
The resulting figure represents eigenvalues of sPCA (denoted lambda-i with i = 1,...,r, where lambda-1
is the highest positive eigenvalue, and lambda-r is the highest negative eigenvalue.

This figure is useful to assess whether a given score
of entities contains relatively enough variability and spatial structuring to be interpreted.
For instance, in the tutorial example, lambda-1 clearly is the largest eigenvalue in terms of variance and of spatial
autocorrelation, and can be well distinguished from all the other eigenvalues. Hence, only
the first global structure, associated to lambda-1, should be interpreted.

##########################################

Global and local tests
If the alternative hypothesis is "greater", a p-value is estimated as: (number of random values equal to or greater than the observed one + 1)/(number of permutations + 1). The null hypothesis is rejected if the p-value is less than the significance level. If the alternative hypothesis is "less", a p-value is estimated as: (number of random values equal to or less than the observed one + 1)/(number of permutations + 1). Again, the null hypothesis is rejected if the p-value is less than the significance level. 

```{r message=FALSE, cache=TRUE}

# Need to replace "NA"s in the genind data table with 0s.
#Strata1_genepop@tab <- na.replace(Strata1_genepop@tab, 0, na.rm=TRUE)
#
#myCode: Phil's above na.replace does not work - unused argument na.rm....

#obj1 <- tab(obj, NA.method="mean") # this converts missing data (NA's) to the mean value for the population

#myCode: Phil replaced missing values with zeros, which seems to be causing problems/not working. I'll try scaling the data as I did above for PCAs - however, the above sPCA object is done with the original data... unscaled... is this okay?

#Strata1_scaled <- scaleGen(Strata1_genepop, NA.method="mean")

myGtest <- global.rtest(Strata1_scaled, mySpca$lw, nperm=9999) # can start with 99 permutations to test

myGtest
a=paste0("observation = ",round(myGtest$obs,5))
b=paste0("alternative hypothesis = ",myGtest$alter)
c=paste0("based on ",myGtest$rep," replicates")
d=paste0("simulated pvalue = ",myGtest$pvalue)


plot(myGtest, main="Global Structure Strata 1")
text(0.0156,3000,a, pos=4)
text(0.0156,2500,b, pos=4)
text(0.0156,2000,c, pos=4)
text(0.0156,1500,d, pos=4)
myGtest

# The figure shows a histogram of permuted test statistics and indicates the observed statistics by a black dot and a segment. in the example (tutorial-spca.pdf), the plot clearly shows that the oberved test statistic is NOT larger than most simulated values, leading to a likely ACCEPTANCE of the null hypothesis of absence of spatial structure.```
```

local test
```{r message=FALSE, cache=TRUE}

myLtest <- local.rtest(Strata1_scaled,mySpca$lw, nperm = 9999) #recommend 9999 permutations; test with 99
myLtest
a=paste0("observation = ",round(myLtest$obs,5))
b=paste0("alternative hypothesis = ",myLtest$alter)
c=paste0("based on ",myLtest$rep," replicates")
d=paste0("simulated pvalue = ",myLtest$pvalue)

plot(myLtest, main="Local Structure Strata 1")
text(0.0165,3000,a, pos=4)
text(0.0165,2500,b, pos=4)
text(0.0165,2000,c, pos=4)
text(0.0165,1500,d, pos=4)
myLtest
```

I think this is a good stopping point for now... Phil goes on to make 2D and 3D plots and whatnot - but in the presence of significant structure. 

I'll test this for my southern AK large populations as a last-ditch effort... maybe sample size plays a role




```{r}
title="SAK"

SAK_genepop$other$xy$x<-as.numeric(SAK_genepop$other$xy$x)
SAK_genepop$other$xy$y<-as.numeric(SAK_genepop$other$xy$y)

SAK_genepop$other$xy$x<-jitter(SAK_genepop$other$xy$x, factor = .5)
SAK_genepop$other$xy$y<-jitter(SAK_genepop$other$xy$y, factor = .5)

#NAs are automatically replaced to mean allele frequency:
mySpca <- spca(SAK_genepop, ask=T, type=1, scannf=F, nfposi = 4, nfnega = 0, scale=T) # method used by LL


# Positive eigenvalues (on the left) correspond to global structures, while negative eigenvalues (on the right) indicate local patterns.
barplot(mySpca$eig, main="sPCA eigenvalues South_AK Large Pops",
col=spectral(length(mySpca$eig)))
legend("topright", fill=spectral(2),
leg=c("Global structures", "Local structures"))
abline(h=0,col="grey")

sp <- screeplot(mySpca,main = "SAK Spatial and Variance Components of the Eigenvalues")

# WHEN THIS DOESN'T WORK, it's because the number of eigenvectors doesn't match the number of expected (?) eigenvectors. For 88 samples, there should be 87 eigenvectors, so if mySpca$eig = anything other than 87, there will be an error. The only way I've found to fix this is to change the factor parameter when the lat/lon positions are jittered, then re-run sPCA.
# Re-running it over and over again with the same factor can also result in different numbers of eigenvalues, so you can just re-run this section until it works.

```

spatial and variance components of the eigenvalues (tutorial p. 13-14)
The resulting figure represents eigenvalues of sPCA (denoted lambda-i with i = 1,...,r, where lambda-1
is the highest positive eigenvalue, and lambda-r is the highest negative eigenvalue.

This figure is useful to assess whether a given score
of entities contains relatively enough variability and spatial structuring to be interpreted.
For instance, in the tutorial example, lambda-1 clearly is the largest eigenvalue in terms of variance and of spatial
autocorrelation, and can be well distinguished from all the other eigenvalues. Hence, only
the first global structure, associated to lambda-1, should be interpreted.

##########################################

Global and local tests
If the alternative hypothesis is "greater", a p-value is estimated as: (number of random values equal to or greater than the observed one + 1)/(number of permutations + 1). The null hypothesis is rejected if the p-value is less than the significance level. If the alternative hypothesis is "less", a p-value is estimated as: (number of random values equal to or less than the observed one + 1)/(number of permutations + 1). Again, the null hypothesis is rejected if the p-value is less than the significance level. 

```{r message=FALSE, cache=TRUE}

# Need to replace "NA"s in the genind data table with 0s.
#SAK_genepop@tab <- na.replace(SAK_genepop@tab, 0, na.rm=TRUE)
#SAK_genepop@tab <- na.replace(SAK_genepop@tab, 0)

#myCode: Phil's above na.replace does not work - unused argument na.rm....

#obj1 <- tab(obj, NA.method="mean") # this converts missing data (NA's) to the mean value for the population

#myCode: Phil replaced missing values with zeros, which seems to be causing problems/not working. I'll try scaling the data as I did above for PCAs - however, the above sPCA object is done with the original data... unscaled... is this okay?

#SAK_scaled <- scaleGen(SAK_genepop, NA.method="mean")

#myGtest <- global.rtest(SAK_genepop$tab, mySpca$lw, nperm=999) # can start with 99 permutations to test
myGtest <- global.rtest(SAK_scaled, mySpca$lw, nperm=9999) # can start with 99 permutations to test

myGtest
a=paste0("observation = ",round(myGtest$obs,5))
b=paste0("alternative hypothesis = ",myGtest$alter)
c=paste0("based on ",myGtest$rep," replicates")
d=paste0("simulated pvalue = ",myGtest$pvalue)


plot(myGtest, main="Global Structure SAK Large Pops")
text(0.021,2400,a, pos=4)
text(0.021,2000,b, pos=4)
text(0.021,1500,c, pos=4)
text(0.021,1000,d, pos=4)
myGtest

# The figure shows a histogram of permuted test statistics and indicates the observed statistics by a black dot and a segment. in the example (tutorial-spca.pdf), the plot clearly shows that the oberved test statistic is NOT larger than most simulated values, leading to a likely ACCEPTANCE of the null hypothesis of absence of spatial structure.```
```

local test
```{r message=FALSE, cache=TRUE}
myLtest <- local.rtest(SAK_scaled,mySpca$lw, nperm = 9999) #recommend 9999 permutations; test with 99
myLtest
a=paste0("observation = ",round(myLtest$obs,5))
b=paste0("alternative hypothesis = ",myLtest$alter)
c=paste0("based on ",myLtest$rep," replicates")
d=paste0("simulated pvalue = ",myLtest$pvalue)

plot(myLtest, main="Local Structure SAK Large Pops")
text(0.0225,3000,a, pos=4)
text(0.0225,2500,b, pos=4)
text(0.0225,2000,c, pos=4)
text(0.0225,1500,d, pos=4)
myLtest
```

